\apendice{Lista de publicações e participações em conferências}

Neste apêndice são listadas trabalhos publicados e contribuições científicas em conferências relacionados direta ou indiretamente a esta tese.

\subsection*{Publicações em periódicos como primeiro autor}

\begin{itemize}
	\item \underline{NISHIKAWA, A. S.}; SANTOFIMIA M. J.; SIETSMA J.; GOLDENSTEIN H. Influence of bainite reaction on the kinetics of carbon redistribution during the Quenching and Partitioning process. \textbf{Acta Materialia}, v. 142, p. 142--151, jan 2018. DOI: \href{http://dx.doi.org/10.1016/j.actamat.2017.09.048}{10.1016/j.actamat.2017.09.048}.

	\item \underline{NISHIKAWA, A. S.}; MIYAMOTO G.; FURUHARA T.; TSCHIPTSCHIN A. P.; GOLDENSTEIN H. Phase transformation mechanisms during Quenching and Partitioning of a Ductile Cast Iron. \textbf{submetido à Acta Materialia}
\end{itemize}

\subsection*{Publicações em periódicos em coautoria}

\begin{itemize}
	\item MELADO, A. C.; \underline{NISHIKAWA, A. S.}; VIEIRA, E. A.; GOLDENSTEIN, H.; Effect of microstructure on fatigue behaviour of advanced high strength ductile cast iron produced by quenching and partitioning process. \textbf{International Journal of Fatigue}, v. 104, p. 397–407, nov 2017. DOI: \href{http://dx.doi.org/10.1016/j.ijfatigue.2017.07.009}{10.1016/j.ijfatigue.2017.07.009}.

	\item ARIZA, E. A.; \underline{NISHIKAWA, A. S.}; GOLDENSTEIN, H.; TSCHIPTSCHIN, A. P. Characterization and methodology for calculating the mechanical properties of a TRIP-steel submitted to hot stamping and quenching and partitioning (Q\&P). \textbf{Materials Science and Engineering: A}, v. 671, p. 54–69, aug 2016. DOI: \href{http://dx.doi.org/10.1016/j.msea.2016.06.038}{10.1016/j.msea.2016.06.038}.
\end{itemize}

\subsection*{Trabalhos apresentados em conferências}

\begin{itemize}
	\item \underline{NISHIKAWA, A. S.}; MELADO, A. C.; RAMIREZ, A. J.; GOLDENSTEIN, H.; Quenching \& Partitioning heat treatment on a ductile cast iron: competition between martensite/austenite carbon partition and bainite reaction -- microstructure and kinetic measurements. \textbf{PTM 2015 - Proceedings of the International Conference on Solid-Solid Phase Transformations in Inorganic Materials 2015}. Whistler, Canada. p. 89–90, 2015.

	\item MELADO, A. C. \underline{NISHIKAWA, A. S.}; VIEIRA E. A.; GOLDENSTEIN, H.; Quenching \& partitioning heat treatment on a ductile iron: Competition between martensite/austenite carbon partition and bainite reaction -- Mechanical properties. \textbf{PTM 2015 - Proceedings of the International Conference on Solid-Solid Phase Transformations in Inorganic Materials 2015}. Whistler, Canada. p. 89–90, 2015.

	\item \underline{NISHIKAWA, A. S.}; MELADO, A. C.; ARIZA, E. A.; TSCHIPTSCHIN A. P.; GOLDENSTEIN, H.; Quenching and Partitioning on Ductile Cast Irons. \textbf{TMS 2016}. Nashville, EUA. 2016.

	\item \underline{NISHIKAWA A. S.}; GOLDENSTEIN H. Effect of bainite reaction and carbides precipitation on the carbon redistribution during Q\&P process. \textbf{Alemi 2017}. Beijing, China. 2017.

	\item \underline{NISHIKAWA A. S.} pyebsd: an open-source tool for processing EBSD data and determining accurate orientation relationship. \textbf{Alemi 2018}. Metz, França. 2018.
\end{itemize}